Active-contours driven registration method for structure-informed segmentation of diffusion MR images

### 2015-04-09 Publications/2015-NeuroImage/05-results.tex
updates and standalone figures

\begin{figure*}
    \centering
    \resizebox{\textwidth}{!}{%
      \begin{tikzpicture}
        \node[inner sep=10pt, draw=black!40](fig03b) at (0,7.9)
          {\hspace*{20pt}\includegraphics[width=\linewidth]{figure05A}};
        \node[inner sep=10pt, draw=black!40](fig03c) at (0,0)
          {\hspace*{20pt}\includegraphics[width=\linewidth]{figure05B}};
        \node[circle, text=black!75] at (-9.4,10.6) {\Huge \textbf{A}};
        \node[circle, text=black!75] at (-9.4,3.5) {\Huge \textbf{B}};
      \end{tikzpicture}
    }%
  \caption{A. Visual assessment of the results on the low resolution sets:
    ``gyrus'' (top-left), ``L'' (top-right), ``ball'' (bottom-left),
    and ``box'' at (bottom-right).
  In yellow color, the recovered contours after registration are represented.
  Our method showed high accuracy, as it demonstrates the almost exact location of the registered
    contours with respect to their ground truth position depicted in green.
  Partial volume effect turns segmentation of the sulci a challenging problem with voxel-wise
    clustering methods, but it is successfully segmented with our method.
  B. Quantitative evaluation of registration error in terms of average Hausdorff distance of
    surfaces at low (left) and high (right) resolutions, demonstrating that the error is
    consistently below the voxel size.
    }\label{fig:phantom}
\end{figure*}
A total of 1200 experiments (4 phantom types $\times$ 150 random warpings $\times$ 2 resolutions) were
  run using the workflow given in \autoref{fig:evphantoms}.
For each experiment, the misregistration error was measured using the Hausdorff distance
  (see \autoref{sec:experiments_evaluation}) between the theoretical $\gammaset_\text{true}$ and
  the estimation done by \emph{regseg} ($\hat{\gammaset}_{test}$).
The results showed a consistent and high accuracy, below the image resolution.
\autoref{fig:phantom} (block C) presents the violin plots by model type corresponding
  to the two sets of resolutions of generated phantoms.
In order to relate average misregistration error to the resolution of the moving image,
  we proceeded as follows.
First, we confirmed that the vertex-wise error distributions were skewed using a Shapiro-Wilk test of
  normality.
All the distributions of errors under test (4 phantom types $\times$ 2 resolutions) resulted
  non-normal with $p<0.001$.
Consequently, we used the non-parametric Wilcoxon signed-rank test along with Bonferroni
  correction for multiple comparisons ($N=150$, for each phantom type).
Averaged errors resulted significantly lower than voxel size with $p < (0.001 / 150)$
  for all the tests (4 phantom types $\times$ 2 resolutions).
Since statistical tests may not be conclusive enough, we also computed the confidence intervals,
  reported in \autoref{tab:ci_phantom}.

@@

\begin{figure*}
    \centering
    \resizebox{\textwidth}{!}{%
      \begin{tikzpicture}
        \node[inner sep=15pt, draw=black!40](fig05a) at (0,11)
          {\hspace*{20pt}\includegraphics[width=\linewidth]{figure06A}};
        \node[inner sep=15pt, draw=black!40](fig05b) at (0,0)
          {\hspace*{20pt}\includegraphics[width=\linewidth]{figure06B}};
        % \node[inner sep=5pt, draw=black!40](fig03c) at (0,0)
        %   {\includegraphics[width=\linewidth]{figure03-c}};
        \node[circle, text=black!75] at (-9.5,17) {\Huge \textbf{A}};
        \node[circle, text=black!75] at (-9.5,3) {\Huge \textbf{B}};
        % \node[circle, text=black!75] at (-8.8,3.4) {\Huge \textbf{C}};
      \end{tikzpicture}
    }%
	\caption{A. Example of one report for visual assessment, automatically generated by the evaluation instrument.
    Each view shows one component of the input image (in this case, the \gls*{fa} map), the ground-truth location
    of the surfaces (green contours), and the resulting surfaces with the method under test (yellow contours).
  First two rows show axial slices for \emph{regseg} and the \acrfull*{t2b} method, and the last two rows
    show corresponding sagittal views.
  Coronal view is omitted since it is the least informative due to the the directional property
    of distortions.
	Red arrows point to regions where \emph{regseg} overperformed the \gls*{t2b} method.
  B. Violin plots of error distributions of each surface, with indication of the voxel size of the \gls*{dmri} images
    (1.25 mm), and supporting the improved results of \emph{regseg} in the proposed settings.
	}\label{fig:results_real}
\end{figure*}

>>>>

\begin{figure*}
  \centering
  \includestandalone[width=\linewidth]{figure05}
  \caption{A. Visual assessment of the results on the low resolution sets:
    ``gyrus'' (top-left), ``L'' (top-right), ``ball'' (bottom-left),
    and ``box'' at (bottom-right).
  In yellow color, the recovered contours after registration are represented.
  Our method showed high accuracy, as it demonstrates the almost exact location of the registered
    contours with respect to their ground truth position depicted in green.
  Partial volume effect turns segmentation of the sulci a challenging problem with voxel-wise
    clustering methods, but it is successfully segmented with our method.
  B. Quantitative evaluation of registration error in terms of average Hausdorff distance of
    surfaces at low (left) and high (right) resolutions, demonstrating that the error is
    consistently below the voxel size.
    }\label{fig:phantom}
\end{figure*}
A total of 1200 experiments (4 phantom types $\times$ 150 random warpings $\times$ 2 resolutions) were
  run using the workflow given in \autoref{fig:evphantoms}.
For each experiment, the misregistration error was measured using the Hausdorff distance
  (see \autoref{sec:experiments_evaluation}) between the theoretical $\gammaset_\text{true}$ and
  the estimation done by \emph{regseg} ($\hat{\gammaset}_{test}$).
The results showed a consistent and high accuracy, below the image resolution.
\autoref{fig:phantom} (block C) presents the violin plots by model type corresponding
  to the two sets of resolutions of generated phantoms.
In order to relate average misregistration error to the resolution of the moving image,
  we proceeded as follows.
First, we confirmed that the vertex-wise error distributions were skewed using a Shapiro-Wilk test of
  normality.
All the distributions of errors under test (4 phantom types $\times$ 2 resolutions) resulted
  non-normal with $p<0.001$.
Consequently, we used the non-parametric Wilcoxon signed-rank test along with Bonferroni
  correction for multiple comparisons ($N=150$, for each phantom type).
Averaged errors resulted significantly lower than voxel size with $p < (0.001 / 150)$
  for all the tests (4 phantom types $\times$ 2 resolutions).
Since statistical tests may not be conclusive enough, we also computed the confidence intervals,
  reported in \autoref{tab:ci_phantom}.

@@

\begin{figure*}
  \centering
  \includestandalone[width=\linewidth]{figure06}
  \caption{A. Example of one report for visual assessment, automatically generated by the evaluation instrument.
    Each view shows one component of the input image (in this case, the \gls*{fa} map), the ground-truth location
    of the surfaces (green contours), and the resulting surfaces with the method under test (yellow contours).
  First two rows show axial slices for \emph{regseg} and the \acrfull*{t2b} method, and the last two rows
    show corresponding sagittal views.
  Coronal view is omitted since it is the least informative due to the the directional property
    of distortions.
	Red arrows point to regions where \emph{regseg} overperformed the \gls*{t2b} method.
  B. Violin plots of error distributions of each surface, with indication of the voxel size of the \gls*{dmri} images
    (1.25 mm), and supporting the improved results of \emph{regseg} in the proposed settings.
	}\label{fig:results_real}
\end{figure*}

### 2015-04-09 Publications/2015-NeuroImage/08-acknowledgements.tex
updates and standalone figures

DZ was supported by the Swiss National Science Foundation under grants PBELP2\_137727 
  and P300P2\_147778, and NSF-DMS 1418812
This study is supported by: the Spain's Ministry of Science and Innovation
  (projects TEC-2013-48251-C2-2-R and INNPACTO XIORT), Comunidad de Madrid (TOPUS) and
  European Regional Development Funds; the Center for Biomedical Imaging
  (CIBM) of the Geneva and Lausanne Universities and the EPFL, as well as the
  Leenaards and Louis Jeantet foundations.

>>>>

DZ was supported by the Swiss National Science Foundation under grants PBELP2-137727 
  and P300P2-147778, and NSF-DMS 1418812
This study is supported by: the Spain's Ministry of Science and Innovation
  (projects TEC-2013-48251-C2-2-R and INNPACTO XIORT), Comunidad de Madrid (TOPUS) and
  European Regional Development Funds; the Center for Biomedical Imaging
  (CIBM) of the Geneva and Lausanne Universities and the EPFL, as well as the
  Leenaards and Louis Jeantet foundations.
